Task 1 

```{r}
install.packages("tidyverse")
library(readr)        # to import tabular data (e.g. csv)
library(dplyr)        # to manipulate (tabular) data
library(ggplot2)      # to visualize data
library(sf)           # to handle spatial vector data
library(terra)        # To handle raster data
library(lubridate)    # To handle dates and times
```

```{r}
wildschwein_BE <- read_delim("wildschwein_BE_2056.csv",",")
```

```{r}
wildschwein_BE <- st_as_sf(wildschwein_BE, coords = c("E", "N"), crs = 2056, remove = FALSE)
wildschwein_BE

```

Task 2 : Getting an overview
Calculate the time difference between subsequent rows

```{r}
wildschwein <- mutate(wildschwein_BE,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec")
wildschwein
```


```{r}
wildschwein %>% group_by(TierID) %>% summarise(mean_timelag = mean(timelag,na.rm = T))
```
Creating visualisation plot : 

```{r}
ggplot(data = wildschwein_BE) +geom_point(mapping = aes(x = DatetimeUTC, y = TierID), color = "blue")
```

    How many individuals were tracked?
    3

    For how long were the individual tracked? Are there gaps?
    002A : about 1 year
    016A : a little bit less than 8 months
    O18A : about 8 months
    
    Were all individuals tracked concurrently or sequentially?
    concurrently
    
    What is the temporal sampling interval between the locations?
    002A : 290 sec
    016A : 2.5 sec
    018A : 1600 sec


Task 3 : Deriving movement parameters I: Speed

```{r}
E2 <- lead(wildschwein_BE$E, 1)
N2 <- lead(wildschwein_BE$N, 1)
steplength <- sqrt((wildschwein_BE$E - E2)^2 + (wildschwein_BE$N - N2)^2)
wildschwein <- mutate(wildschwein_BE,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec", steplength)
wildschwein

```

Animals'speed : 

the animal's speed is defined by the steplength by seconde

in theory : steplength/timelag = m/s

```{r}
speed <- wildschwein$steplength/wildschwein$timelag
wildschwein <- mutate(wildschwein_BE,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec", steplength, speed)
wildschwein
```

we want to now the mean speed per animal 

```{r}
wildschwein %>% group_by(TierID) %>% summarise(mean_speed = mean(speed,na.rm = T))
```
Task 4 : Cross-scale movement analysis

```{r}
library(readr)
caro <- read_csv("caro60.csv", col_types = cols(CollarID = col_number(), DatetimeUTC = col_datetime(format = "%Y-%m-%dT%H:%M:%SZ"), E = col_number(), N = col_number()))
View(caro)
nrow(caro)
```

The locations are stored in EPSG 2056

```{r}
caro_3 <- slice(caro, seq(from = 1, to = 200, by = 3))
nrow(caro_3)
```

```{r}
caro_6 <- slice(caro, seq(from = 1, to = 200, by = 6))
nrow(caro_6)
```

```{r}
caro_9 <- slice(caro, seq(from = 1, to = 200, by = 9))
nrow(caro_9)
```

analyse of caro

```{r}
#timelag
caro <- mutate(caro,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec")
#steplength
E2 <- lead(caro$E, 1)
N2 <- lead(caro$N, 1)
steplength <- sqrt((caro$E - E2)^2 + (caro$N - N2)^2)
caro <- mutate(caro, steplength)
#speed
speed <- caro$steplength/caro$timelag
caro <- mutate(caro, speed)
caro %>% summarise(mean_speed = mean(speed,na.rm = T))
```

analse of caro_3

```{r}
#timelag
caro_3 <- mutate(caro_3,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec")
#steplength
E2 <- lead(caro_3$E, 1)
N2 <- lead(caro_3$N, 1)
steplength <- sqrt((caro_3$E - E2)^2 + (caro_3$N - N2)^2)
caro_3 <- mutate(caro_3, steplength)
#speed
speed <- caro_3$steplength/caro_3$timelag
caro_3 <- mutate(caro_3, speed)
caro_3 %>% summarise(mean_speed = mean(speed,na.rm = T))
```

analyse of caro_6

```{r}
#timelag
caro_6 <- mutate(caro_6,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec")
#steplength
E2 <- lead(caro_6$E, 1)
N2 <- lead(caro_6$N, 1)
steplength <- sqrt((caro_6$E - E2)^2 + (caro_6$N - N2)^2)
caro_6 <- mutate(caro_6, steplength)
#speed
speed <- caro_6$steplength/caro_6$timelag
caro_6 <- mutate(caro_6, speed)
caro_6 %>% summarise(mean_speed = mean(speed,na.rm = T))
```

analyse of caro_9

```{r}
#timelag
caro_9 <- mutate(caro_9,timelag = as.numeric(difftime(lead(DatetimeUTC),DatetimeUTC)), units = "sec")
#steplength
E2 <- lead(caro_9$E, 1)
N2 <- lead(caro_9$N, 1)
steplength <- sqrt((caro_9$E - E2)^2 + (caro_9$N - N2)^2)
caro_9 <- mutate(caro_9, steplength)
#speed
speed <- caro_9$steplength/caro_9$timelag
caro_9 <- mutate(caro_9, speed)
caro_9 %>% summarise(mean_speed = mean(speed,na.rm = T))
```
```{r}
View(caro_3)
View(caro_6)
View(caro_9)
```

comparing caro and caro_3 in a line plot

```{r}
ggplot() + geom_point(data = caro, mapping = aes (x = E, y = N), color = "blue") + geom_path(data = caro, mapping = aes (x = E, y = N), color = "blue") + geom_point(data= caro_3, mapping = aes (x = E, y =N), color = "red") + geom_path(data = caro_3, mapping = aes (x = E, y = N), color = "red") + ggtitle("Comparing original- with 3 minutes resampled data", subtitle = "Trajectory : Blue = 1 min, Red = 3 min") + theme(plot.title=element_text(hjust=0.5), plot.subtitle=element_text(hjust=0.5))
```
#Comment : I couldn't find out how to put the legends on the side. As a graph has to be understandable, i put a subtitle which explains the colors on the graph. 

comparing caro and caro_6 in a line plot

```{r}
ggplot() + geom_point(data = caro, mapping = aes (x = E, y = N), color = "blue") + geom_path(data = caro, mapping = aes (x = E, y = N), color = "blue") + geom_point(data= caro_6, mapping = aes (x = E, y =N), color = "red") + geom_path(data = caro_6, mapping = aes (x = E, y = N), color = "red") + ggtitle("Comparing original- with 6 minutes resampled data", subtitle = "Trajectory : Blue = 1 min, Red = 6 min") + theme(plot.title=element_text(hjust=0.5), plot.subtitle=element_text(hjust=0.5))
```


comparing caro and caro_9 in a line plot

```{r}
ggplot() + geom_point(data = caro, mapping = aes (x = E, y = N), color = "blue") + geom_path(data = caro, mapping = aes (x = E, y = N), color = "blue") + geom_point(data= caro_9, mapping = aes (x = E, y =N), color = "red") + geom_path(data = caro_9, mapping = aes (x = E, y = N), color = "red") + ggtitle("Comparing original- with 9 minutes resampled data", subtitle = "Trajectory : Blue = 1 min, Red = 9 min") + theme(plot.title=element_text(hjust=0.5), plot.subtitle=element_text(hjust=0.5))
```

comparing derived speed at different sampling intervals

```{r}
ggplot() + geom_line(data = caro, mapping = aes(x = DatetimeUTC, y = speed), color = "blue") +geom_line(data = caro_3, mapping = aes(x = DatetimeUTC, y = speed), color = "red") + geom_line(data = caro_6, mapping = aes(x = DatetimeUTC, y = speed), color = "green") + geom_line(data = caro_9, mapping = aes(x = DatetimeUTC, y = speed), color = "orange")+ ggtitle("Comparing original- with 9 minutes resampled data", subtitle = "Blue : 1 min, Red : 3 min, Green : 6 min, Orange : 9 min") + theme(plot.title=element_text(hjust=0.5), plot.subtitle=element_text(hjust=0.5)) + labs (x = "Time", y = "Speed")
```

Interpret the line plot, what do the different lines for the different temporal granularities tell you? 
- the bigger the intervall sampling, the smoother the speed.The 1 min intervall gives us more infos on the speed of the animal. Ex : at 9, the animal was maybe running away from som predator. At 10, it had to hurry for some reason, etc... the bigger the interval, the less exact information we have about its deplacements. 

